---
title: "Question R02.1"
author: "Yifan Wang"
date: "2023-10-22"
output: html_document
---

!!!This part of the code should be right at the end of the workshop 2.3 code. 
this code can run ONLY after running ALL the "weather forecast" part of workshop2.3 code.!!!

In other words, this code should be copied in workshop2.3.rmd at the end, and run it last

This part is about using the model provided by workshop2.3 to predict the temperature in 2040
```{r}
# Create a data frame with a "Time" column, covering the months from 2040 to 2041
new_data <- data.frame(Time = seq(2040, 2041, by = 1/12))

# Make predictions using the linear model
linear_prediction <- predict(tempmodelcv, newdata = new_data)

# Make predictions using the polynomial model
polynomial_prediction <- predict(tempmodelcvint, newdata = new_data)

# Create a data frame to store the predictions
predictions_df <- data.frame(Time = new_data$Time,
                             Linear_Model_Prediction = linear_prediction,
                             Polynomial_Model_Prediction = polynomial_prediction)

# Print the prediction results as a list
print(predictions_df)

```

This part uses the ARIMA model for prediction
```{r}
# Load the required library
if (!require("forecast")) install.packages("forecast")

# Create a time series object
temperature_ts <- ts(temperature2$MA, frequency = 12)  # Assuming the data is monthly

# Fit an ARIMA model
arima_model <- auto.arima(temperature_ts)

# View a summary of the ARIMA model
summary(arima_model)

# Make forecasts
forecast_values <- forecast(arima_model, h = 12*25)  # Forecast the next 24 years (12 months/year * 25 years)

# Print the forecasted values
print(forecast_values)
```
This part is cross-validation of the ARIMA model. 
attention: running time is about 3 minutes.
```{r}
# Select the first time series
selected_ts <- temperature_ts

# Set cross-validation parameters
n_splits <- 5  # Split the data into 5 parts

# Initialize performance metric list
mse_scores <- numeric(n_splits)

# Perform cross-validation
for (i in 1:(n_splits-1)) {
  # Split the data into training and testing sets
  train_data <- window(selected_ts, end = 167 * i / n_splits)
  test_data <- window(selected_ts, start = 167 * i / n_splits + 1)
  
  # Fit an ARIMA model
  arima_model <- auto.arima(train_data)
  
  # Make predictions
  forecast_values <- forecast(arima_model, h = length(test_data))
  
  # Calculate mean squared error
  mse_scores[i] <- mean((test_data - forecast_values$mean)^2)
}

# Output cross-validation performance metrics
cat("Mean Squared Error (MSE):", mse_scores[1:(n_splits-1)], "\n")
cat("Average MSE:", mean(mse_scores[1:(n_splits-1)]), "\n")
```
This is the result that should appear:

Mean Squared Error (MSE): 0.1799287 0.3330269 0.1127717 0.1524568 
Average MSE: 0.194546 

SARIMA_model 
```{r}
# Load the required library
if (!require("forecast")) install.packages("forecast")

# Create a time series object
temperature_ts <- ts(temperature2$MA, frequency = 12)  # Assuming the data is monthly

# Specify SARIMA order and seasonal order
p <- 1  # Replace with the appropriate non-seasonal autoregressive order
d <- 1  # Replace with the appropriate non-seasonal differencing order
q <- 1  # Replace with the appropriate non-seasonal moving average order
P <- 1  # Replace with the appropriate seasonal autoregressive order
D <- 1  # Replace with the appropriate seasonal differencing order
Q <- 1  # Replace with the appropriate seasonal moving average order
# Specify SARIMA order and seasonal order
seasonal_period <- 12  # Assuming monthly data

# Create the seasonal order list
seasonal_order <- list(order = c(P, D, Q), period = seasonal_period)

# Fit a SARIMA model
sarima_model <- Arima(temperature_ts, order = c(p, d, q), seasonal = seasonal_order)


# View a summary of the SARIMA model
summary(sarima_model)

# Make forecasts
forecast_values <- forecast(sarima_model, h = 12*25)  # Forecast the next 24 years (12 months/year * 25 years)

# Print the forecasted values
print(forecast_values)

```


